### 2020-02-20 README.Rmd
Replacing the very large newsgroup data with some abstracts.

`newsgroup_stm` is an example topic model trained with the data `newsgroup5` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` and LDA/CTM models from `topicmodels`.

@@

```{r example}
newsgroup_stm
```

@@

```{r createtest}
oolong_test <- create_oolong(newsgroup_stm)
oolong_test
```

@@

For example, `newsgroup_stm` was generated with the corpus `newsgroup5$text`

```{r newgroup5}
library(tibble)
newsgroup5
```

@@

```{r createtest2}
oolong_test <- create_oolong(newsgroup_stm, newsgroup5$text)
oolong_test
```

@@

```{r step0, eval = FALSE}
dfm(newsgroup5$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 5, max_docfreq = 1000) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> newsgroup5_dfm
docvars(newsgroup5_dfm, "title") <- newsgroup5$title
newsgroup5_dfm %>% convert(to = "stm", omit_empty = FALSE) -> newsgroup5_stm
newsgroup_stm <- stm(newsgroup5_stm$documents, newsgroup5_stm$vocab, data =newsgroup5_stm$meta, K = 10, seed = 42)
```

@@

```{r step1}
oolong_test_rater1 <- create_oolong(newsgroup_stm, newsgroup5$text)
```

@@

`newsgroup_warplda` is a Warp LDA object trained with the same dataset as the `newsgroup_stm`

```{r warplda}
newsgroup_warplda
```

@@

```{r warplda2}
### Just word intrusion test.
oolong_test <- create_oolong(newsgroup_warplda)
oolong_test
```

```{r warplda3}
newsgroup5_dfm
```

```{r warplda4}
oolong_test <- create_oolong(newsgroup_warplda, newsgroup5$text, input_dfm = newsgroup5_dfm)
oolong_test
```

>>>>

`abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` and LDA/CTM models from `topicmodels`.

@@

```{r example}
abstracts_stm
```

@@

```{r createtest}
oolong_test <- create_oolong(abstracts_stm)
oolong_test
```

@@

For example, `abstracts_stm` was generated with the corpus `abstracts$text`

```{r newgroup5}
library(tibble)
abstracts
```

@@

```{r createtest2}
oolong_test <- create_oolong(abstracts_stm, abstracts$text)
oolong_test
```

@@

```{r step0, eval = FALSE}
dfm(abstracts$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 5, max_docfreq = 1000) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> abstracts_dfm
docvars(abstracts_dfm, "title") <- abstracts$title
abstracts_dfm %>% convert(to = "stm", omit_empty = FALSE) -> abstracts_stm
abstracts_stm <- stm(abstracts_stm$documents, abstracts_stm$vocab, data =abstracts_stm$meta, K = 10, seed = 42)
```

@@

```{r step1}
oolong_test_rater1 <- create_oolong(abstracts_stm, abstracts$text)
```

@@

`abstracts_warplda` is a Warp LDA object trained with the same dataset as the `abstracts_stm`

```{r warplda}
abstracts_warplda
```

@@

```{r warplda2}
### Just word intrusion test.
oolong_test <- create_oolong(abstracts_warplda)
oolong_test
```

```{r warplda3}
abstracts_dfm
```

```{r warplda4}
oolong_test <- create_oolong(abstracts_warplda, abstracts$text, input_dfm = abstracts_dfm)
oolong_test
```
